---
title: "Machine Learning"
author: "Adam Caffrey"
date: "20/12/2020"
output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(kableExtra)
```

This is a simple overview of machine learning in R. It shall make use of the tidymodels libraries and is intended to be a personal reminder and help sheet for any new learners. I intend to continuously improve the site over time as I better learn the features of tidymodels!

The table below shows the libraries included with tidymodels and the methods most commonly used by me.

```{r echo=FALSE}
col_a <- c(rep("rsample", 3),
           "parsnip", 
           rep("recipes", 5),
           rep("workflows", 2),
           "tune", 
           rep("yardstick", 2),
           "broom", 
           "dials", 
           "corrr")
col_b <- c("initial_split", "training", "testing",
           "various parsnip",
           "recipe", "step_<name>", "prep", "bake", "juice",
           "add_recipe", "add_model",
           "various tune",
           "metrics", "roc_auc",
           "tidy",
           "various dials",
           "corrr_stuff")
col_c <- c("Splits data into a testing and training set", 
           "returns the training data set", 
           "returns the testing data set",
           "pending description",
           "pending description", "pending description", "pending description", "pending description", "pending description",
           "pending description", "pending description",
           "pending description",
           "pending description", "pending description",
           "pending description",
           "pending description",
           "pending description")

collapse_rows_dt <- data.frame("Packages" = col_a, "Methods" = col_b, "Description" = col_c)
kbl(collapse_rows_dt, align = "l") %>%
  collapse_rows(columns = 1:2, valign = "top") %>% 
  kable_paper(full_width=T, html_font = "sans-serif") %>% 
  scroll_box(width = "100%", height = "200px")
  

```

***

Additional useful libraries

```{r echo=FALSE}
col_a <- c("corrplot")
col_b <- c("corrplot")
col_c <- c("creates a pretty correlation plot")

collapse_rows_dt <- data.frame("Packages" = col_a, "Methods" = col_b, "Description" = col_c)
kbl(collapse_rows_dt, align = "l") %>%
  collapse_rows(columns = 1:2, valign = "top") %>% 
  kable_paper(full_width=T, html_font = "sans-serif") %>% 
  scroll_box(width = "100%", height = "200px")

```

## Data Preprocessing

In order to determine which machine learning algorithm should be employed you must study your data! Creating tidy data is fundamental to machine learning. The following steps must be understood:

1. [Dealing with missingness](./missingness.html)   
2. [Correlations within data](./correlation.html)   
3. [How sampling works](./sampling.html)

## Other Useful Concepts

1. [Parallel Processing](./parallel_processing.html)   
2. [Metrics](./model_performance.html)

## Supervised Learning

Supervised machine learning requires labelled data...

1. [Linear Regression](./linear_regression.html)
2. [Logistic Regression](./logistic_regression.html)   


## Unsupervised Learning

***
[Additional Resources](./resources.html)
