---
title: "ORDER BY, DISTINCT and WHERE"
author: "Adam Caffrey"
date: "06/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sqldf)
library(kableExtra)
```

This demo will use the **iris** dataset.

This page shall incorporate the additional filtering statements ORDER BY, DISTINCT and WHERE on top of the already-established SQL commands.   

ORDER BY allows output to be ordered by ascending (ASC) or descending (DESC), based on one feature or multiple. 

**Example:** What are the top ten longest petal lengths in the iris dataset?   

```{r}
sqldf("
  SELECT `Petal.Length` FROM iris
  ORDER BY `Petal.Length` DESC
  LIMIT 10;
")
```
**Example:** What are the species of the three shortest sepal widths?

```{r}
sqldf("
  SELECT Species FROM iris
  ORDER BY `Sepal.Width` ASC
  LIMIT 3;
")
```

Distinct is used when you want to return unique values, it is one of the most often-used statements:

**Example:** What iris species exist in the iris dataset?

```{r}
sqldf("SELECT DISTINCT Species FROM iris;")
```

**Example:** What are 10 unique combinations of iris species and petal lengths ordered by the longest sepals?

```{r}
sqldf("
  SELECT DISTINCT Species, `Petal.Length` FROM  iris
  ORDER BY `Sepal.Length` DESC
  LIMIT 10;
")
```

Finally, where allows you to set conditionals. The syntax for this are as follows:   
```{r, echo=FALSE}
col1 <- c("=", ">", "<", ">=", "<=", "<>")
col2 <- c("Equal", "Greater than", "Less than", "Greater than or equal to", "Less than or equal to", "Not equal to")

data.frame(col1, col2) %>% 
  kable(col.names = c("Symbol", "Description")) %>% 
  kable_styling(full_width = F)
  
  
```

The WHERE statement gives you a lot of control over your data. This statement allows much more complicated questions be answered.

**Example:** What are the species and petal lengths of iris' which have petal widths greater than 1.5?


```{r}
sqldf("
  SELECT Species, `Petal.Width` FROM iris
  WHERE `Petal.Width` > 2.2;
")
```


**Example:** How many data points have a petal width of exactly 2?

```{r}
sqldf("
  SELECT COUNT(Species) FROM iris
  WHERE `Petal.Width` = 2;
")
```













#