---
title: "SUM, AVERAGE, COUNT, MIN and MAX"
author: "Adam Caffrey"
date: "06/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sqldf)
```

This demo will use the **iris** dataset.

When selecting data, aggregated output can be returned. The most common aggregation functions are: SUM, AVERAGE, COUNT, MIN and MAX.   

**Example 1:** What is the sum of all the petal widths?

```{r}
sqldf("
  SELECT SUM(`Petal.Width`) FROM iris;      
")
```
**Example 2:** What is the average sepal length?

```{r}
sqldf("
  SELECT AVG(`Sepal.Length`) FROM iris;      
")
```
**Example 3:** How many rows are in the iris dataset?

```{r}
sqldf("
  SELECT COUNT(Species) FROM iris  
")
```
**Example 4:** What is the smallest petal length?

```{r}
sqldf("
  SELECT MIN(`Petal.Length`) FROM iris;      
")
```
**Example 5:** How long is the longest petal?

```{r}
sqldf("
  SELECT MAX(`Petal.Length`) FROM iris;      
")
```

All functions are relatively easy to implement, the difficulty is realising when you should be using each!
