---
title: "JOIN"
author: "Adam Caffrey"
date: "07/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(magrittr)
library(readr)
library(sqldf)
library(kableExtra)

```

This demo will use two custom datasets; **df1** and **df2**:

## data
```{r echo = FALSE}
df1 <- data.frame("id" = 1:8,
                  "a" = c("name 1", "name 2", "name 3", "name 4", "name 5", "name 6", "name 7", "name 8"))
df2 <- data.frame("id" = 1:6,
                  "a" = c("cat", "dog", "piano", "bear", "yakult", "air fryer"))

```

```{r}
df1 %>% 
  kable() %>% 
  kable_styling(full_width = F)

df2 %>% 
  kable() %>% 
  kable_styling(full_width = F)
```

Unfortunately, not all joins are available when using **sqldf**, those which are will be shown here. The 4 main joins are:   
1. INNER JOIN   
2. OUTER JOIN   
3. LEFT JOIN   
4. RIGHT JOIN   

## LEFT JOIN

The left join takes all the data in the first (left) dataset and any matching values in the right (second) table

```{r}
sqldf("
  SELECT df1.a, df2.a
  FROM df1
  LEFT JOIN df2 ON df1.id=df2.id;
")
```

## RIGHT JOIN

The RIGHT JOIN takes all the data from the second (right) dataset and any matching entries from the left (first). **Not currently supported by sqldf**.

```{r, eval = FALSE}
sqldf("
  SELECT df1.name, df2.name 
  FROM df1
  RIGHT JOIN df2.id=df1.id
")
```

## INNER JOIN

The INNER JOIN keeps any data which is in both tables.

```{r}
sqldf("
  SELECT df1.a, df2.a
  FROM df1
  INNER JOIN df2 ON df1.id=df2.id
")
```

## FULL OUTER JOIN

FULL OUTER JOIN keeps all data, in both tables, whether they match or not. **Not currently supported by sqldf**.

```{r, eval = FALSE}
sqldf("
  SELECT df1.name, df2.name 
  FROM df1
  OUTER JOIN df2.id=df1.id
")
```
