---
title: "GROUP BY"
author: "Adam Caffrey"
date: "07/01/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sqldf)
library(dplyr)
sw <- starwars[,1:11]
```

This demo uses both the **iris** and **dplyr::starwars** datasets. The startwars dataset has list columns removed.

The GROUP BY statement allows data to be aggregated in subsets. 

**Example:** What is the average petal length of each iris species?

```{r}
sqldf("
  SELECT Species, AVG(`Petal.Length`) AS average_petal_length
  FROM iris
  GROUP BY Species;
")

```

**Example:** For the virginica and setosa species what is the median sepal length? List the longest first.
```{r}
sqldf("
  SELECT MEDIAN(`Sepal.Width`) AS mean_sepal_width, Species FROM iris
  WHERE Species IN ('virginica','setosa')
  GROUP BY Species 
  ORDER BY mean_sepal_width DESC
")
```
**Example:** From the star wars dataset, what is the average character height from each homeworld? List the 7 with the shortest average.
```{r}
sqldf("
  SELECT AVG(height) AS average_height, homeworld FROM sw  
  WHERE homeworld NOT NULL AND
  height NOT NULL
  GROUP BY homeworld
  ORDER BY average_height ASC
  LIMIT 7
")
```

**Example:** What is the maximum height from species from each homeworld? List the top 3
```{r}
sqldf("
  SELECT MAX(height) AS max_height, homeworld FROM sw
  WHERE homeworld NOT NULL AND
  height NOT NULL
  GROUP BY homeworld
  ORDER BY max_height DESC
  LIMIT 3
")
```


