---
title: "SELECT, FROM and LIMIT"
author: "Adam Caffrey"
date: "06/01/2021"
output: html_document
---

<script src="./script.js"></script>
<link rel = "stylesheet" href = "stylesheet.css">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sqldf)
```

This demo will use the **iris** dataset.

The SELECT statement is used to retrieve data from a table. In its simplest form, without a table, it will return what you pass it:

```{r}
sqldf("
  SELECT 1 + 5;
")
```

As a general rule, you will want to SELECT data FROM a table. If no table is present then, for MySQL, it is good practice to use DUAL as a dummy table. If you do have a table, an individual column (field) can be selected. Selecting the Species column from the iris dataset:

<div class="fold o">
```{r}
sqldf("
  SELECT Species FROM iris;
")
```
</div>

That is a lot of output! This is where the LIMIT statement comes in. You can LIMIT the number of entries returned:

```{r}
sqldf("
  SELECT Species FROM iris LIMIT 5;      
")
```

Multiple columns can be selected at once but the same number of entries must be returned for each. When a field name contains a "." the name must be surrounded by `, " or []:

```{r}
sqldf("
  SELECT `Petal.Length`, Species FROM iris LIMIT 8;      
")
```

