---
title: "LIKE and NOT NULL"
author: "Adam Caffrey"
date: "07/01/2021"
output: html_document
---

```{r setup, include=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(sqldf)
library(kableExtra)
library(dplyr)
sw <- starwars[,1:11]
```

This demo will use the **starwars** dataset from the **[dplyr](https://dplyr.tidyverse.org/)** library with list columns dropped, renamed to sw.

regex is a powerful tool in SQL. It is one of the more common uses day-to-day. The following special characters are particularly important:

```{r, echo = FALSE}
col1 <- c("%", "_", "[]", "^", "-")
col2 <- c("zero or multiple characters", 
          "single character",
          "any single character within brackets",
          "any character not in brackets",
          "range of characters")
data.frame("Character" = col1, 
           "Definition" = col2) %>% 
  kable() %>% 
  kable_styling(full_width = F)

```

The best way to understand how this works is with some practical(ish) examples.

**Example 1:** How many characters have eye colours beginning with a b?
```{r}
sqldf("
  SELECT COUNT(name) FROM sw
  WHERE eye_color LIKE 'b%';
")
```
**Example 2:** List all the planets containing "oo"
```{r}
sqldf("
  SELECT DISTINCT homeworld FROM sw
  WHERE homeworld LIKE '%oo%';
")
```

The following example uses NOT NULL to filter rows containing NA.

**Example 3:** Who is the youngest character from any planet beginning with N?
```{r}
sqldf("
  SELECT name, homeworld, birth_year FROM sw
  WHERE homeworld LIKE 'N%'
  AND birth_year NOT NULL
  ORDER BY birth_year ASC
  LIMIT 1;
")
```
**Example 5:** What is the average height of characters whose names don't end in an "a"
```{r}
sqldf("SELECT AVG(height) AS average_height FROM sw
      WHERE name NOT LIKE '%a'")
```

